Enforced Invariant Confluence

### 2018-04-30 doc/paper/sections/segmented_invariant_confluence.tex
Added a note about segment suggestion.

\subsection{Discussion}
There are a couple of things worth noting about segmented
\invariantconfluence{}, its system model, and its decision procedure. First,
\invariantconfluence{} is a very coarse-grained property. If an object is
\invariantconfluent{}, then we can replicate it with no coordination. If it is
not \invariantconfluent{}, then we have no guarantees. There's no in-between.
Segmented \invariantconfluence{}, on the other hand, is a much more
fine-grained property that can be applied to applications with varying degrees
of complexity. Segmented \invariantconfluence{} provides guarantees to complex
applications that require a large number of segments and to simple applications
with a smaller number of segments, whereas \invariantconfluence{} only provides
guarantees to applications that can be segmented into a single segment.

@@

>>>>

\subsection{Discussion}
There are a couple of things worth noting about segmented
\invariantconfluence{}, its system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

@@

Fifth, while a segmented \invariantconfluence{} decision procedure can help
decide whether or not an object is segmented \invariantconfluent{}, it cannot
currently help construct the segmentation. In the future, we plan to explore
ways by which we can automatically suggest segmentations to the application
designer.
